---
title: "Simulation Study - thAV"
author: "Anonymous"
date: "19 02 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#1. Import & Definition of Functions
```{r}
require("devtools") # to install thav.glasso
library("devtools")
install("../../thav.glasso") # contains the estimator and simulation methods
require("thav.glasso")
require("MASS") # to sample from multivariate normal
require("igraph") # to generate graphs
require("stargazer") # to produce latex outputs
require("huge") # contains adjacency matrix generation and StARS + RIC estimation
require("matrixcalc") # to compute eigenvalues
require("glasso") # to compute the graphical lasso

# graph design
igraph_options(vertex.size       =2,
               vertex.label.cex  = 1,
               edge.width        = 1 ,
               vertex.label      ="",
               vertex.color      ="black",
               vertex.frame.color=NA,
               edge.color        ="coral1")
```

#2. Compare several methods in $F_1$-score
In this simulation study we want to investigate the performance of the thAV in comparison to 
  1. the oracle graphical lasso estimator that uses the regularization parameter that maximizes the $F_1$-score,
  2. the StARS estimator,
  3. the RIC estimator.

## 2.1. Results from the Main Paper
```{r}
# F_1-score
set.seed(182)
comparisonf1( 300, 200, latex=TRUE, graph="random")
set.seed(182)
comparisonf1(300, 200, latex=TRUE, graph="scale-free")

set.seed(123)
comparisonf1( 200, 300, latex=TRUE, graph="random")
set.seed(123)
comparisonf1(200, 300, latex=TRUE, graph="scale-free")

set.seed(312)
comparisonf1( 400, 200, latex=TRUE, graph="random")
set.seed(312)
comparisonf1(400, 200, latex=TRUE, graph="scale-free")


set.seed(13)
comparisonf1( 300, 200, graph="scale-free", lambda=2, latex=TRUE)
set.seed(233)
comparisonf1( 300, 400, graph="scale-free", lambda = 2, latex=TRUE)
set.seed(234)
comparisonf1( 400, 200, graph="scale-free", lambda = 2, latex=TRUE)

# compare recovered graphs
set.seed(121)
graph_comparison(300, 200)


# thav using lambda=2 for a random graph:
set.seed(84)
simulation_thavf1(n_seq=c(300, 200, 400), d_seq=c(200, 300, 200), graph="random", lambda=2, latex=TRUE)
set.seed(30)
simulation_thavf1(n_seq=c(300, 200, 300), d_seq=c(100, 200, 300), graph="random", lambda=2, latex=TRUE)
```


##2.2. Results from the Supplement
```{r}
# compute F_1-score
set.seed(93)
comparisonf1(300, 100, latex=TRUE, graph="random")
set.seed(93)
comparisonf1(300, 100, latex=TRUE, graph="scale-free")

set.seed(19)
comparisonf1(200, 200, latex=TRUE, graph="random")
set.seed(19)
comparisonf1(200, 200, latex=TRUE, graph="scale-free")

set.seed(32)
comparisonf1(300, 300, latex=TRUE, graph="random")
set.seed(32)
comparisonf1(300, 300, latex=TRUE, graph="scale-free")

# compare recovered graphs
set.seed(59)
graph_comparison(200, 300)
set.seed(65)
graph_comparison(400, 200)

set.seed(14)
graph_comparison(300, 200, "scale-free")
set.seed(43)
graph_comparison(200, 300, "scale-free")
set.seed(65)
graph_comparison(400, 200, "scale-free")
```

#3. Recovery of significant edges
We want to investigate if thAV recovers the $50$ most significant edges.

##3.1. Exemplary runs of thAV
First, we compare the most significant edge ($\operatorname{top}_1$), the $50$th most significant edge ($\operatorname{top}_{50}$), $6C\hat{r}$ and the percentage of recovered top $50$ edges for several settings.
###3.1.1 Results from the Main Paper
```{r}
set.seed(19)
thav_topvalues(n_seq=c(300, 200, 400), d_seq=c(200, 300, 200))
set.seed(32)
thav_topvalues(c(300, 200, 400), c(200, 300, 200), graph="scale-free")
```

###3.1.2 Results from the Supplement
```{r}
set.seed(21)
thav_topvalues(n_seq=c(300, 200, 300), d_seq=c(100, 200, 300))
set.seed(78)
thav_topvalues(n_seq=c(300, 200, 300), d_seq=c(100, 200, 300), graph="scale-free")
```

##3.2. Compare top-edges recovery performance
Next, we extend the analysis by a thoroughly simulation study that compares the recovery of top $50$ edges of the thAV with the StARS and RIC in several settings.
###3.2.1. Results from the Main Paper
```{r}
set.seed(33)
recovery_topvalues(n_seq=300, d_seq=200, num_reps=50, latex=TRUE)
set.seed(23)
recovery_topvalues(n_seq=200, d_seq=300, num_reps=50, latex=TRUE)
set.seed(22)
recovery_topvalues(n_seq=400, d_seq=200, num_reps=50, latex=TRUE)

set.seed(32)
recovery_topvalues(n_seq=300, d_seq=200, num_reps=50, latex=TRUE, graph="scale-free")
set.seed(49)
recovery_topvalues(n_seq=200, d_seq=300, num_reps=50, latex=TRUE, graph="scale-free")
set.seed(43)
recovery_topvalues(n_seq=400, d_seq=200, num_reps=50, latex=TRUE, graph="scale-free")
```

###3.2.2. Results from the Supplement
```{r}
set.seed(99)
recovery_topvalues(n_seq=300, d_seq=100, latex=TRUE)
set.seed(63)
recovery_topvalues(n_seq=200, d_seq=200, latex=TRUE)
set.seed(73)
recovery_topvalues(n_seq=300, d_seq=300, latex=TRUE)

set.seed(123)
recovery_topvalues(n_seq=300, d_seq=100, latex=TRUE, graph="scale-free")
set.seed(30)
recovery_topvalues(n_seq=200, d_seq=200, latex=TRUE, graph="scale-free")
set.seed(20)
recovery_topvalues(n_seq=300, d_seq=300, latex=TRUE, graph="scale-free")
```


#4. Dependence on $C$
In this study, we want to show that the thAV reacts insensitive on the specific choice of $C$.

##4.1. F_1-Matrix 
In particular, we generate a "$F_1$-matrix whose entries $F_{i,j}$ correspond to the $F_1$-score of the thAV based on $C_i$ and the thAV based on $C_j$, where $(C_1,...,C_s)$ is a sequence of different $C>0$.

###4.1.1. Results from the Main Paper
```{r}
set.seed(145)
comparison_similarity( 300, 200, latex=TRUE)
```

###4.1.2. Results from the Supplement
```{r}
set.seed(203)
comparison_similarity( 200, 300, latex=TRUE)
set.seed(11)
comparison_similarity( 400, 200, latex=TRUE)
```


###4.1.3. Results for scale-free graphs
```{r}
set.seed(32)
comparison_similarity(300, 200, latex=TRUE, graph="scale-free")
set.seed(99)
comparison_similarity(200, 300, latex=TRUE, graph="scale-free")
set.seed(73)
comparison_similarity(400, 200, latex=TRUE, graph="scale-free")
```


##4.2. Visualization of the graphs based on different C
This code visualizes the different thAV estimations for different choices of $C$.
(Does not occure in the Main paper or the Supplement)
```{r}
set.seed(27)
visualization_differentC(300, 200)
set.seed(23)
visualization_differentC(200, 200)
set.seed(267)
visualization_differentC(400, 200)
set.seed(43)
visualization_differentC(1000, 200)
```


##4.3. Adaptation of the Threshold
Further, we show that the proposed threshold, $t:=3C\hat{r}$ adapts on the chosen $C$ in thAV. This code provides the data, whereas the plots are generated by adaptation_threshold.ipynb.
###4.3.1. Results from the Main Paper
```{r}
set.seed(142)
adaptation_threshold(300, 200)
set.seed(23)
adaptation_threshold(300, 200, C=0.2)
set.seed(54)
adaptation_threshold(300, 200, C=0.4)
```

###4.3.2. Results from the Supplement
```{r}
set.seed(142)
adaptation_threshold(300, 200, graph="scale-free")
set.seed(23)
adaptation_threshold(300, 200, C=0.2, graph="scale-free")
set.seed(54)
adaptation_threshold(300, 200, C=0.4, graph="scale-free")


set.seed(100)
adaptation_threshold(200, 300, C=0.3)
set.seed(29)
adaptation_threshold(200, 300, C=0.2)
set.seed(42)
adaptation_threshold(200, 300, C=0.4)
set.seed(100)
adaptation_threshold(200, 300, C=0.3, graph="scale-free")
set.seed(29)
adaptation_threshold(200, 300, C=0.2, graph="scale-free")
set.seed(42)
adaptation_threshold(200, 300, C=0.4, graph="scale-free")

set.seed(234)
adaptation_threshold(400, 200, C=0.3)
set.seed(7)
adaptation_threshold(400, 200, C=0.2)
set.seed(33)
adaptation_threshold(400, 200, C=0.4)
set.seed(234)
adaptation_threshold(400, 200, C=0.3, graph="scale-free")
set.seed(7)
adaptation_threshold(400, 200, C=0.2, graph="scale-free")
set.seed(33)
adaptation_threshold(400, 200, C=0.4, graph="scale-free")
```


#4. Stability in the Graphs Density
Furthermore, we show that thAV estimation remains, independently of the graphs density, superior over StARS and RIC.
We do this by comparing the resulting $F_1$-score for several settings and graph densities.

##4.1. Results from the Supplement
```{r}
d <- 200
#seq_density <- c(2/d, 3/d, 4/d)
set.seed(142)
comparison_density( 300, d, 2/d, latex=TRUE)
set.seed(142)
comparison_density( 300, d, 3/d, latex=TRUE)
set.seed(142)
comparison_density( 300, d, 4/d, latex=TRUE)

d <- 300
set.seed(33)
comparison_density( 200, d, 2/d, latex=TRUE)
set.seed(19)
comparison_density(200, d, 3/d, latex=TRUE)
set.seed(21)
comparison_density(200, d, 4/d, latex=TRUE)

d <- 200
set.seed(33)
comparison_density( 400, d, 2/d, latex=TRUE)
set.seed(19)
comparison_density(400, d, 3/d, latex=TRUE)
set.seed(21)
comparison_density(400, d, 4/d, latex=TRUE)
```


#5. Large-scale Performance of thAV
The thAV is computational efficent and we can readily apply it for larger problems (increase of the dimensionality). 
In particular, we consider $n=500$ and $d\in \{600, 700, ...,1000\}$ and the corresponding $F_1$-score of the thAV.
##5.1. Results from the Supplement
```{r}
set.seed(172)
performance_thav(600, num_reps=20)
set.seed(172)
performance_thav(600, num_reps=20, graph="scale-free")

set.seed(76)
performance_thav(700, num_reps=20)
set.seed(76)
performance_thav(700, num_reps=20, graph="scale-free")

set.seed(42)
performance_thav(800, num_reps=20)
set.seed(42)
performance_thav(800, num_reps=20, graph="scale-free")

set.seed(79)
performance_thav(900, num_reps=20)
set.seed(79)
performance_thav(900, num_reps=20, graph="scale-free")

set.seed(55)
performance_thav(1000, num_reps=20)
set.seed(55)
performance_thav(1000, num_reps=20, graph="scale-free")
```


#6. Distribution of the absolute values of $\Theta$
A major drawback of the graph generation methods is the difference in the absolute value of precision matrix entries between random and scale-free graphs.
Here, we generate the data that will be used by visualization_weights.ipynb to plot the histograms of the absolute values of the precision matrix entries.
#6.1. Generation of the .csv-files 
```{r}
set.seed(32)
weight_dist( 200, num_reps=50)
set.seed(30)
weight_dist( 200, num_reps=50, graph="scale-free")

set.seed(43)
weight_dist(300, num_reps=50)
set.seed(99)
weight_dist(300, num_reps=50, graph="scale-free")

set.seed(90)
weight_dist(500, num_reps=50)
set.seed(39)
weight_dist(500, num_reps=50, graph="scale-free")
```

#6.2. Run .ipynb-script
