---
title: "Simulation Study - thAV"
author: "Anonymous"
date: "22 10 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#1. Import & Definition of Functions
```{r}
require("devtools") # to install thav.glasso
install("../../thav.glasso") # contains the estimator and simulation methods
library(thav.glasso)
load_libraries() # loads all required libraries

# graph design
igraph_options(vertex.size       =2,
               vertex.label.cex  = 1,
               edge.width        = 1 ,
               vertex.label      ="",
               vertex.color      ="black",
               vertex.frame.color=NA,
               edge.color        ="coral1")

restart_R <- function()
{
  rm(list = ls())
  .rs.restartR()
}
```

#2. Compare several methods in $F_1$-score
In this experiment investigate the performance of the thAV in comparison to 
  1. the oracle graphical lasso estimator that uses the regularization parameter that maximizes the $F_1$-score,
  2. the StARS estimator,
  3. the scaled lasso estimator,
  4. the TIGER estimator,
  5. the rSME estimator (tuned via eBIC),
  6. the SCIO estimatior tuned via 
    6.1 CV;
    6.2 a bregman criterion.
    
Note, that we split many computations into several parts due to limited computational ressources.
## 2.1. Results from the Main Paper
```{r}
####################
### random graph ###
####################
set.seed(43)
simu_f1_split(300, 200, 1)
set.seed(99)
simu_f1_split(300, 200, 2)
set.seed(900)
simu_f1_split(300, 200, 3, num_reps=5)
simu_f1(300, 200)

set.seed(5)
simu_f1_split(200, 300, 1)
set.seed(9)
simu_f1_split(200, 300, 2)
set.seed(93)
simu_f1_split(200, 300, 3, num_reps=5) 
simu_f1(200, 300)


set.seed(309)
simu_f1_split(400, 200, 1)
set.seed(43)
simu_f1_split(400, 200, 2)
set.seed(32)
simu_f1_split(400, 200, 3, num_reps=5)
simu_f1(400, 200)


########################
### scale-free graph ###
########################
set.seed(400)
simu_f1_split(300, 200, 1, graph="scale-free")
set.seed(81)
simu_f1_split(300, 200, 2, graph="scale-free")
set.seed(3)
simu_f1_split(300, 200, 3, num_reps=5, graph="scale-free")
simu_f1(300, 200, "scale-free", 3)

set.seed(34)
simu_f1_split(200, 300, 1, graph="scale-free")
set.seed(2)
simu_f1_split(200, 300, 2, graph="scale-free")
set.seed(9)
simu_f1_split(200, 300, 3, num_reps=5, graph="scale-free")
simu_f1(200, 300, "scale-free", 3)


set.seed(9)
simu_f1_split(400, 200, 1, graph="scale-free")
set.seed(481)
simu_f1_split(400, 200, 2, graph="scale-free")
set.seed(16)
simu_f1_split(400, 200, 3, num_reps=5, graph="scale-free")
simu_f1(400, 200, "scale-free", 3)
```


##2.2. Results from the Supplement
More settings from the Supplement...
```{r}
####################
### random graph ###
####################
set.seed(3)
simu_f1_split(300, 100, 1)
set.seed(50)
simu_f1_split(300, 100, 2)
set.seed(80)
simu_f1_split(300, 100, 3, num_reps=5)
simu_f1(300, 100, num_parts=3)

set.seed(66)
simu_f1_split(200, 200, 1)
set.seed(691)
simu_f1_split(200, 200, 2) 
set.seed(81)
simu_f1_split(200, 200, 3, num_reps=5)
simu_f1(200, 200) 

set.seed(24)
simu_f1_split(300, 300, 1)
set.seed(2)
simu_f1_split(300, 300, 2)
set.seed(90)
simu_f1_split(300, 300, 3, num_reps=5)
simu_f1(300, 300)


########################
### scale-free graph ###
########################
set.seed(4)
simu_f1_split(300, 100, 1, graph="scale-free")
set.seed(11)
simu_f1_split(300, 100, 2, graph="scale-free")
set.seed(77)
simu_f1_split(300, 100, 3, num_reps=5, graph="scale-free")
simu_f1(300, 100, graph="scale-free")

  set.seed(12)
simu_f1_split(200, 200, 1, graph="scale-free")
set.seed(62)
simu_f1_split(200, 200, 2, graph="scale-free")
set.seed(93)
simu_f1_split(200, 200, 3, graph="scale-free", num_reps=5)
simu_f1(200, 200, graph="scale-free")

  set.seed(15)
  simu_f1_split(300, 300, 1, graph="scale-free")
  set.seed(83)
  simu_f1_split(300, 300, 2, graph="scale-free")
set.seed(55)
simu_f1_split(300, 300, 3, graph="scale-free", num_reps=5)
simu_f1(300, 300, graph="scale-free")
```


The following chunk of code computes visualizations of recovered graphs in each setting with each method.
```{r}
set.seed(43)
graph_comparison(300, 200)
set.seed(59)
graph_comparison(200, 300)
set.seed(65)
graph_comparison(400, 200)

set.seed(14)
graph_comparison(300, 200, "scale-free")
set.seed(82)
graph_comparison(200, 300, "scale-free")
set.seed(65)
graph_comparison(400, 200, "scale-free")
```


#3. Recovery of significant edges
Next, we investigate if thAV recovers the 20% of the most significant edges, that is, the 20% of edges (i,j) with largest absolute value $\vert \Theta_{ij}\vert$.

##3.1. Exemplary runs of thAV
First, we compare the most significant edge ($\operatorname{top}_1$), the $20\%$ of the most significant edges, $4C\hat{r}$ and the percentage of recovered top $20\%$ edges for several settings.

```{r}
set.seed(45)
thav_topvalues(n_seq=c(300, 200, 400), d_seq=c(200, 300, 200))
set.seed(32)
thav_topvalues(c(300, 200, 400), c(200, 300, 200), graph="scale-free")
```

##3.2. Compare top-edges recovery performance
Next, we extend the analysis by a thoroughly simulation study that compares the recovery the $20\%$ of the most significant edges by the thAV with the competing methods in several settings.
```{r}
####################
### random graph ###
####################
set.seed(32)
recovery_topvalues_split(300, 200, num_reps=15, part=1, graph="random")
set.seed(38)
recovery_topvalues_split(300, 200, num_reps=10, part=2, graph="random")

set.seed(32)
recovery_topvalues_split(200, 300, num_reps=10, part=1, graph="random")
set.seed(38)
recovery_topvalues_split(200, 300, num_reps=10, part=2, graph="random")
set.seed(99)
recovery_topvalues_split(200, 300, num_reps=5, part=3, graph="random")

set.seed(32)
recovery_topvalues_split(400, 200, num_reps=15, part=1, graph="random")
set.seed(38)
recovery_topvalues_split(400, 200, num_reps=10, part=2, graph="random")

recovery_topvalues(c(300, 200, 400), c(200, 300, 200))


########################
### scale-free graph ###
########################
set.seed(42)
recovery_topvalues_split(300, 200, num_reps=15, part=1, graph="scale-free")
set.seed(31)
recovery_topvalues_split(300, 200, num_reps=10, part=2, graph="scale-free")

set.seed(29)
recovery_topvalues_split(200, 300, num_reps=10, part=1, graph="scale-free")
set.seed(9)
recovery_topvalues_split(200, 300, num_reps=10, part=2, graph="scale-free")
set.seed(83)
recovery_topvalues_split(200, 300, num_reps=5, part=3, graph="scale-free")

set.seed(32)
recovery_topvalues_split(400, 200, num_reps=15, part=1, graph="scale-free")
set.seed(47)
recovery_topvalues_split(400, 200, num_reps=10, part=2, graph="scale-free")

recovery_topvalues(c(300, 200, 400), c(200, 300, 200), graph="scale-free")
```

#4. Dependence on $C$
In this study, we show that the thAV estimator remains stable in the choice of $C$.

##4.1. F_1-Matrix 
In particular, we generate a ``$F_1$-matrix'' whose entries $F_{i,j}$ correspond to the $F_1$-score of the thAV based on $C_i$ and the thAV based on $C_j$, where $(C_1,...,C_s)$ is a sequence of different $C>0$.

We consider $C\in \{0.5, 0.6, 0.7, 0.8\}$.
###4.1.1. Results from the Main Paper
```{r}
set.seed(145)
comparison_similarity( 300, 200, latex=TRUE, seq_C=c(0.5, 0.6, 0.7, 0.8), num_reps=25)
```

###4.1.2. Results from the Supplement
```{r}
set.seed(203)
comparison_similarity( 200, 300, latex=TRUE, seq_C=c(0.5, 0.6, 0.7, 0.8), num_reps=25)
set.seed(11)
comparison_similarity( 400, 200, latex=TRUE, seq_C=c(0.5, 0.6, 0.7, 0.8), num_reps=25)
```


###4.1.3. Results for scale-free graphs
```{r}
set.seed(32)
comparison_similarity(300, 200, latex=TRUE, graph="scale-free")
set.seed(99)
comparison_similarity(200, 300, latex=TRUE, graph="scale-free")
set.seed(73)
comparison_similarity(400, 200, latex=TRUE, graph="scale-free")
```


##4.2. Visualization of the graphs based on different C
These lines of code visualize the resulting thAV estimations for different choices of $C$.
```{r}
set.seed(40)
visualization_differentC(300, 200)
visualization_differentC(200, 300)
visualization_differentC(400, 200)

set.seed(47)
visualization_differentC(300, 200, graph="scale-free")
visualization_differentC(200, 300, graph="scale-free")
visualization_differentC(400, 200, graph="scale-free")
```


##4.3. Adaptation of the Threshold
Further, we show that the proposed threshold, $t:=C\hat{r}$ adapts on the chosen $C$. This code provides the data, whereas the plots are generated in adaptation_threshold.ipynb.

###4.3.1. Results from the Main Paper
```{r}
set.seed(121)
adaptation_threshold(300, 200)
```


###4.3.2. Results from the Supplement
```{r}
set.seed(102)
adaptation_threshold(300, 200, graph="scale-free")

adaptation_threshold(400, 200)
adaptation_threshold(400, 200, graph="scale-free")
  
adaptation_threshold(200, 300)
adaptation_threshold(200, 300, graph="scale-free")
```

Can we expect a similar behaviour of the thresholded approach for the unregularized (maximum likelihood) estimator? The answer is no. These lines of code generate the data to generate similar plots in adaptation_threshold.ipynb.
```{r}
#####################################################
### Thresholded MLE (unregularized optimization): ###
#####################################################
set.seed(42)
unregularized_threshold(300, 200)
unregularized_threshold(400, 200)

unregularized_threshold(300, 200, graph="scale-free")
unregularized_threshold(400, 200, graph="scale-free")
```


#5. Stability in the Graphs Density
Furthermore, we show that thAV estimation remains, independently of the graphs density, superior to the other methods in terms of $F_1$-score. Hence, the calibration scheme is indeed adaptive, not only to the specific setting of $n, d$, but also to the targets density.

##5.1. Results from the Supplement
```{r}
set.seed(7)
comparison_density_split(300, 200, c(2/200, 4/200), part=1, num_reps=5)
set.seed(30)
comparison_density_split(300, 200, c(2/200, 4/200), part=2, num_reps=5)
set.seed(10)
comparison_density_split(300, 200, c(2/200, 4/200), part=3, num_reps=5)
set.seed(371)
comparison_density_split(300, 200, c(2/200, 4/200), part=4, num_reps=5)
set.seed(67)
comparison_density_split(300, 200, c(2/200, 4/200), part=5, num_reps=5)
comparison_density(300, 200, c(2/200, 4/200), num_parts=5, graph="random")
  
set.seed(4)
comparison_density_split(200, 300, c(2/300, 4/300), part=1, num_reps=5)
set.seed(3)
comparison_density_split(200, 300, c(2/300, 4/300), part=2, num_reps=5)
set.seed(54)
comparison_density_split(200, 300, c(2/300, 4/300), part=3, num_reps=5)
set.seed(34)
comparison_density_split(200, 300, c(2/300, 4/300), part=4, num_reps=5)
set.seed(21)
comparison_density_split(200, 300, c(2/300, 4/300), part=5, num_reps=5)
comparison_density(200, 300, c(2/300, 4/300), num_parts=5, graph="random")


set.seed(50)
comparison_density_split(400, 200, c(2/200, 4/200), part=1, num_reps=5)
set.seed(39)
comparison_density_split(400, 200, c(2/200, 4/200), part=2, num_reps=5)
  set.seed(871)
  comparison_density_split(400, 200, c(2/200, 4/200), part=3, num_reps=5)
set.seed(600)
comparison_density_split(400, 200, c(2/200, 4/200), part=4, num_reps=5)
set.seed(511)
comparison_density_split(400, 200, c(2/200, 4/200), part=5, num_reps=5)
comparison_density(400, 200, c(2/200, 4/200), num_parts=5, graph="random")
```


#6. Large-scale Performance of thAV
The thAV is computational efficent and we can readily apply it for larger problems (increase of the dimensionality). 
In particular, we consider $n=500$ and $d\in \{600, 700, ...,1000\}$ and the corresponding $F_1$-score of the thAV.
##6.1. Results from the Supplement
```{r}
set.seed(172)
performance_thav(600, num_reps=20)
set.seed(172)
performance_thav(600, num_reps=20, graph="scale-free")

set.seed(76)
performance_thav(700, num_reps=20)
set.seed(76)
performance_thav(700, num_reps=20, graph="scale-free")

set.seed(42)
performance_thav(800, num_reps=20)
set.seed(42)
performance_thav(800, num_reps=20, graph="scale-free")

set.seed(79)
performance_thav(900, num_reps=20)
set.seed(79)
performance_thav(900, num_reps=20, graph="scale-free")

set.seed(55)
performance_thav(1000, num_reps=20)
set.seed(55)
performance_thav(1000, num_reps=20, graph="scale-free")
```


#7. Applying the thAV-technique for other estimation methods
In Section 1.1 of the Supplement, we introduced a very general theory. In these experiments, we apply the general framework onto 2 other estimation methods for Gaussian graphical models.

##7.1 thAV on rSME
```{r}
set.seed(76)
simu_thav_others(300, 200, estimator="av_rsme", C=2, lambda=1, num_reps=25, graph="random")
set.seed(54)
simu_thav_others(200, 300, estimator="av_rsme", C=2, lambda=1, num_reps=25, graph="random")
set.seed(40)
simu_thav_others(400, 200, estimator="av_rsme", C=2, lambda=1, num_reps=25, graph="random")

set.seed(944)
simu_thav_others(300, 200, estimator="av_rsme", C=2, lambda=1, num_reps=25, graph="scale-free")
set.seed(11)
simu_thav_others(200, 300, estimator="av_rsme", C=2, lambda=1, num_reps=25, graph="scale-free")
set.seed(83)
simu_thav_others(400, 200, estimator="av_rsme", C=2, lambda=1, num_reps=25, graph="scale-free")
```

##7.2 thAV on sf-glasso
```{r}
set.seed(3)
simu_thav_others(300, 200, estimator="av_sf", C=1.5, lambda=1.5, num_reps=25, graph="random")
set.seed(66)
simu_thav_others(200, 300, estimator="av_sf", C=1.5, lambda=1.5, num_reps=25, graph="random")
set.seed(20)
simu_thav_others(400, 200, estimator="av_sf", C=1.5, lambda=1.5, num_reps=25, graph="random")

set.seed(48)
simu_thav_others(300, 200, estimator="av_sf", C=1.5, lambda=1.5, num_reps=25, graph="scale-free")
set.seed(77)
simu_thav_others(200, 300, estimator="av_sf", C=1.5, lambda=1.5, num_reps=25, graph="scale-free")
set.seed(100)
simu_thav_others(400, 200, estimator="av_sf", C=1.5, lambda=1.5, num_reps=25, graph="scale-free")
```


#8. Distribution of the absolute values of $\Theta$
A major drawback of the graph generation methods that we employ is that the absolute values distribution of the precision matrix entries varies between random and scale-free graphs.  
Here, we generate the data that will be used by the ``visualization_weights.ipynb'' script to plot the histograms of the absolute values of the precision matrix entries.
## 8.1. Results from the Supplement
```{r}
set.seed(32)
weight_dist( 200, num_reps=50)
set.seed(30)
weight_dist( 200, num_reps=50, graph="scale-free")

set.seed(43)
weight_dist(300, num_reps=50)
set.seed(99)
weight_dist(300, num_reps=50, graph="scale-free")

set.seed(90)
weight_dist(500, num_reps=50)
set.seed(39)
weight_dist(500, num_reps=50, graph="scale-free")
```
